Adaptive group-regularized logistic elastic net regression Supplementary material

### 2019-03-06 docs/supplement.Rnw
stability selection in parallel

% set options
<<settings, include=FALSE, echo=FALSE>>=
opts_knit$set(root.dir="..", base.dir="../figs")
opts_chunk$set(fig.align='center', fig.path="../figs/", 
               echo=FALSE, cache=FALSE, message=FALSE)
@

@@

@@

<<>>=
res <- read.table("results/micrornaseq_colorectal_cancer_res3.csv", 
                  stringsAsFactors=FALSE)
medians <- round(apply(res, 2, median), 2)
@
  We compared the estimated multipliers to the estimates by \texttt{GRridge}. 
  Since these results depend on one specific randomisation of the groups, we 
  repeated the procedure 100 times and present the results in Figure 
  \ref{fig:boxplots_micrornaseq_colorectal_cancer_res3_multipliers}. 
  From this figure we see that the estimates for \texttt{gren} are close to one.
  The estimates by \texttt{GRridge} show much more variation. We found no strong
  indication of bias, with median estimated penalty parameters 
  \Sexpr{medians[c(1:3)]} for
  \texttt{GRridge} and \Sexpr{medians[c(4:6)]}; \Sexpr{medians[c(7:9)]},
  and \Sexpr{medians[c(10:12)]} for \texttt{gren} with 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$, respectively.
<<boxplots_micrornaseq_colorectal_cancer_res3_multipliers, fig.cap="Results for the colorectal cancer example with 100 realisations of 3 random groups of features.", out.width="50%", fig.asp=1>>=
@

  We repeated the simulation with ten evenly sized groups. Figure 
  [! figure ref here] presents the estimated penalty multipliers for 100 random 
  splits of the microRNA features into 10 evenly sized groups for 
  \texttt{GRridge} and \texttt{gren} with $\alpha \in \{ 0.05, 0.5, 0.95 \}$. 
  From the Figure we see that \texttt{GRridge} shows more variation around one 
  then the other models. In addition, the median penalty multipliers for the 
  three \texttt{gren} models are all between [! medians here], while the 
  \texttt{GRridge} median estimates range from [! medians here]. This indicates 
  that \texttt{GRridge} suffers from a slight bias in the estimation, while the 
  \texttt{gren} estimates appear to be unbiased.
<<boxplots_micrornaseq_colorectal_cancer_res4_multipliers, fig.cap="Results for the colorectal cancer example with 100 realisations of 10 random groups of features, plotted (a) with outliers, and (b) without outliers.", out.width="100%", fig.asp=1/2>>=
@

@@

>>>>

% set options
<<settings, include=FALSE, echo=FALSE>>=
opts_knit$set(root.dir="..", base.dir="../figs")
opts_chunk$set(fig.align='center', fig.path="../figs/", 
               echo=FALSE, cache=FALSE, message=FALSE, fig.pos='!ht')
@

@@

  \subsection{Additional comparisons}

@@

<<>>=
res <- read.table("results/micrornaseq_colorectal_cancer_res3.csv", 
                  stringsAsFactors=FALSE)
medians <- round(apply(res, 2, median), 2)
@
  We compared the estimated multipliers to the estimates by \texttt{GRridge}. 
  Since these results depend on one specific randomisation of the groups, we 
  repeated the procedure 100 times and present the results in Figure 
  \ref{fig:boxplots_micrornaseq_colorectal_cancer_res3_multipliers}. 
  From this figure we see that the estimates for \texttt{gren} are relatively 
  close to one.
  The estimates by \texttt{GRridge} show more variation. We found no strong
  indication of bias, with median estimated penalty parameters 
  \Sexpr{medians[c(1:3)]} for
  \texttt{GRridge} and \Sexpr{medians[c(4:6)]}; \Sexpr{medians[c(7:9)]},
  and \Sexpr{medians[c(10:12)]} for \texttt{gren} with 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$, respectively.
<<boxplots_micrornaseq_colorectal_cancer_res3_multipliers, fig.cap="Results for the colorectal cancer example with 100 realisations of 3 random groups of features.", out.width="50%", fig.asp=1>>=
@

<<>>=
res <- read.table("results/micrornaseq_colorectal_cancer_res4.csv", 
                  stringsAsFactors=FALSE)
medians <- round(sapply(c("grridge", paste0("gren", 1:3)), function(s) {
  median(as.matrix(res[, grepl(s, colnames(res))]))}), 2)
@
  We repeated the simulation with ten evenly sized groups. Figure 
  \ref{fig:boxplots_micrornaseq_colorectal_cancer_res4_multipliers} presents 
  the estimated penalty multipliers for 100 random 
  splits of the microRNA features into 10 evenly sized groups for 
  \texttt{GRridge} and \texttt{gren} with $\alpha \in \{ 0.05, 0.5, 0.95 \}$. 
  From the Figure we see that \texttt{GRridge} shows more variation around one 
  then the other models. There is no indication of bias: the median penalty 
  multiplier for 
  \texttt{GRridge} is \Sexpr{medians[1]}, while the median multipliers in
  \texttt{gren} are \Sexpr{medians[c(2:4)]} for 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$, respectively.
<<boxplots_micrornaseq_colorectal_cancer_res4_multipliers, fig.cap="Results for the colorectal cancer example with 100 realisations of 10 random groups of features, plotted (a) with outliers, and (b) without outliers.", out.width="100%", fig.asp=1/2>>=
@

@@

  \section{Choice of $\alpha$}	
	Choice of $\alpha$ does matter in Figure 
	\ref{fig:lines_colorectal_lymph_node_gren_auc}.
<<lines_colorectal_lymph_node_gren_auc, fig.cap="Estimated AUC for gren in the (a) colorectal cancer example and the (b) lymph node metastasis example.", out.width="100%", fig.asp=1/2>>=
@
